---
title: "Stars*EU"
subtitle: "Data Visualize - Static"
author: "Lorena Abad"
date: "14.07.2022 updated: `r format(Sys.time(), '%d.%m.%Y')`"
always_allow_html: true
output: 
  github_document: default
  html_document: 
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, fig.showtext = T)
```

# Read DB data

We will first, as usual, connect to the database to be able to access the created tables. 

```{r conn_details, eval = TRUE, message = FALSE, warning = FALSE}
library(DBI)
library(RPostgres)
db_name = "starseu_spacedb"
local_host = "postgresql-starseu.alwaysdata.net"
port_num = 5432
user_name = "starseu"
## Create connection to DB
connection = dbConnect(
  Postgres(), 
  dbname = db_name,
  host = local_host, 
  port = port_num,
  user = user_name, 
  password = rstudioapi::askForPassword("Database password")
)

## Test if connection is successful
ifelse(
  !dbExistsTable(connection, "test"),
  "The connection to the database was not possible.",
  "The connection to the database was successful!"
)
```
Reading the data now should not be much effort, you can expand the code below: 

```{r}
hei = dbReadTable(connection, "hei")
library(sf)
hei_sf = st_read(connection, "hei", geometry_column = "geometry")
curricula = dbReadTable(connection, "curricula")
courses = dbReadTable(connection, "courses")
```

```{r}
dbDisconnect(connection)
```

We can combine all the information of the three tables into one single table to pick information for the sunburst visualization: 

```{r, message = FALSE, warning = FALSE, fig.showtext=TRUE}
extrafont::loadfonts(device = "win")
library(tidyverse)
library(ggplot2)
library(geomtextpath)
library(data.table)
library(ggtext)

# library(ggfx)
courses = left_join(courses, curricula) %>% 
  left_join(hei)  %>% 
  mutate(
    across(
      steam_category,
      .fns = str_to_sentence
    )) %>% 
  filter(
    !is.na(credits)  
  )

steamt_palette = c(
  "#3789C9",
  "#5560A3",
  "#24589b",
  "#D0CECE",
  "#4E9EC7",
  "#FDEA14"
)

coorpfont = "Calibri"
```

# Function to generate sunbursts by giving a curricula_id

```{r, fig.showtext=TRUE}
sunburst_plot = function(id,
                         fontsizescale = 1,
                         labelabb = FALSE) {
  courses_sum = courses %>% 
    filter(curricula_id == id) %>% 
    fill(hei_name, curricula_name,
         .direction = "down") %>%
    mutate(
    curricula_name = str_replace_all(curricula_name, "MSc", "M.Sc.")
    ) %>%
  mutate(
    curricula_name = str_replace_all(curricula_name, "BSc", "B.Sc.")
    ) %>%
  mutate(
    curricula_name = str_replace_all(curricula_name, "LLM", "LL.M.")
    ) %>%
    mutate(
      across(
        starts_with("knowledge_"),
        .fns = str_to_sentence
      ),
      ## To sort although it does not work with sunburstR
      steam_factor = fct_relevel(
        fct_expand(
          steam_category, 
          "Science", "Technology", 
          "Engineering", "Arts",
          "Mathematics", "Transversal"
        ),
        "Science", "Technology", "Engineering",
        "Arts", "Mathematics", "Transversal"
      ),
      label = str_c(curricula_name, hei_name, sep = " | "),
      color = case_when(
        steam_category == "Technology" ~ "#5560A3",
        steam_category == "Mathematics" ~ "#4E9EC7",
        steam_category == "Science" ~ "#3789C9",
        steam_category == "Engineering" ~ "#24589b",#"#0C4690",
        steam_category == "Arts" ~ "#D0CECE",
        steam_category == "Transversal" ~ "#FDEA14"
      )
    ) %>%
    group_by(steam_factor, knowledge_domain,
             knowledge_area, label, color) %>%
    summarize(
      credits = sum(credits, na.rm = TRUE)
    ) %>% 
    ungroup()
  
  lev1 = courses_sum %>% 
    group_by(steam_factor, color) %>% 
    summarise(
      tot_credits1 = sum(credits)
    ) %>% 
    ungroup() %>% 
    mutate(
      ymax = cumsum(tot_credits1), 
      ymin = lag(ymax, n = 1, default = 0), 
      ylab = (ymax+ymin)/2
    ) %>% 
    mutate(
      steam_factor_abb= case_when(
        steam_factor == "Science" ~ "Sc.",
        steam_factor == "Technology" ~ "Tech.",
        steam_factor == "Engineering" ~ "Eng.",
        steam_factor == "Arts" ~ "Arts",
        steam_factor == "Mathematics" ~ "Math.",
        steam_factor == "Transversal" ~ "Trans."
      ),
      label = paste0(
          steam_factor,
          "\n(ECTS: ", tot_credits1, ")"),
      label_nocred = steam_factor, 
      label_abb = paste0(
          steam_factor_abb,
          "\n(", tot_credits1, ")"),
    )
  
  # setDT(lev1)[tot_credits1 <= 2, label := LETTERS[.I]]
  
  if (nrow(lev1) == 1) {
      lev1 = lev1 %>% add_row(
        steam_factor = " ", tot_credits1 = 0,
        ymin = lev1$ymax, ymax = lev1$ymax, 
        ylab = lev1$ylab, 
        label = " ", label_nocred = " ",
        color = "white"
      )
  }

  lev2 = courses_sum %>% 
    group_by(steam_factor, knowledge_domain, color) %>% 
    summarise(
      tot_credits2 = sum(credits)
    ) %>% 
    left_join(
      select(
        lev1, 
        steam_factor,
        tot_credits1,
        color
      )
    ) %>% 
    ungroup() %>% 
    mutate(
      ymax = cumsum(tot_credits2), 
      ymin = lag(ymax, n = 1, default = 0) ,
      ylab = (ymax+ymin)/2
    ) %>% 
    filter(!is.na(knowledge_domain))
  
  # setDT(lev2)[tot_credits2 <= 3, label := letters[.I]]
  lev2 = lev2 %>% mutate(
    knowledge_domain_abb = case_when(
      knowledge_domain == "Humanities" ~ "Hum.",
      knowledge_domain == "Management" ~ "Mgmt.",
      knowledge_domain == "Innovation" ~ "Innov.",
      knowledge_domain == "Statistics" ~ "Stats.",
      knowledge_domain == "Analysis" ~ "Analy--\nsis",
      knowledge_domain == "Mechatronics" ~ "Mecha--\ntronics",
      knowledge_domain == "Business and economics" ~ "Bus. & Ec.",
      knowledge_domain == "Internship" ~ "Interns.",
      knowledge_domain == "Aerospace engineering" ~ "Aerospace Eng.",
      knowledge_domain == "Electrical engineering" ~ "Elec. Eng.",
      knowledge_domain == "Sustainability" ~ "Sust.",
      knowledge_domain == "Manufacturing" ~ "Manuf.",
      knowledge_domain == "Calculus" ~ "Calc.",
      knowledge_domain == "Algebra" ~ "Alg.",
      knowledge_domain == "Social sciences" ~ "Social sc.",
      knowledge_domain == "System science" ~ "Syst. sc.",
      knowledge_domain == "Environmental science" ~ "Env. sc.",
      TRUE ~ knowledge_domain
    ),
      label = case_when(
        100*tot_credits2/sum(tot_credits1) <= 4 ~ paste0(
          str_wrap(knowledge_domain, 10),
          "\n(ECTS: ", tot_credits2, ")"),
        TRUE ~ paste0(
          knowledge_domain,
          "\n(ECTS: ", tot_credits2, ")")),
      label_nocred = case_when(
        100*tot_credits2/sum(tot_credits1) <= 4 ~ 
          str_wrap(knowledge_domain, 10),
        TRUE ~ knowledge_domain),
      label_abb = paste0(
          str_replace_all(knowledge_domain_abb," ", "\n"),
          "\n(", tot_credits2, ")")
    ) 
  
  if (nrow(lev2) == 1) {
    lev2 = lev2 %>% add_row(
      steam_factor = " ", 
      knowledge_domain = " ",
      tot_credits1 = 0,
      tot_credits2 = 0,
      ymin = lev2$ymax, ymax = lev2$ymax, 
      ylab = lev2$ylab, 
      label = " ", label_nocred = " ",
      color = "white"
    )
  }
  
  lev3 = courses_sum %>% 
    group_by(
      steam_factor,
      knowledge_domain,
      knowledge_area,
      color
    ) %>% 
    summarise(
      tot_credits3 = sum(credits)
    ) %>% 
    left_join(
      select(
        lev2,
        steam_factor,
        knowledge_domain,
        tot_credits1,
        tot_credits2,
        color
      )
    ) %>% 
    ungroup() %>% 
    mutate(
      ymax = cumsum(tot_credits3), 
      ymin = lag(ymax, n = 1, default = 0),
      ylab = (ymax+ymin)/2
    ) %>% 
    filter(!is.na(knowledge_area))
  
  # setDT(lev3)[tot_credits3 <= 2, label := LETTERS[.I]]
  lev3 = lev3 %>% mutate(
      knowledge_area_abb = case_when(
      knowledge_area == "Project management" ~ "Proj. mgmt.",
      knowledge_area == "Innovation management" ~ "Inn. mgmt.",
      knowledge_area == "Business law" ~ "Bus. law",
      knowledge_area == "Languages" ~ "Lang.",
      knowledge_area == "Entrepreneurship" ~ "Entrep.",
      knowledge_area == "Material science" ~ "Mat. sc.",
      knowledge_area == "Physical chemistry" ~ "Phys. chem.",
      knowledge_area == "Spacecraft design" ~ "Spacec. design",
      knowledge_area == "Spacecraft propulsion" ~ "Spacec. prop.",
      TRUE ~ knowledge_area
    ),
      label = case_when(
      100*tot_credits3/sum(tot_credits1) <= 4 ~ paste0(
        str_wrap(knowledge_area, 8),
        "\n(ECTS: ", tot_credits3, ")"),
      TRUE ~ paste0(
        knowledge_area,
        "\n(ECTS: ", tot_credits3, ")")),
      label_nocred = case_when(
      100*tot_credits3/sum(tot_credits1) <= 4 ~ 
        str_wrap(knowledge_area, 8),
      TRUE ~ knowledge_area),
      label_abb = paste0(
      str_replace_all(knowledge_area_abb," ", "\n"),
      "\n(", tot_credits3, ")")
  ) 
  
  if (nrow(lev3) == 1) {
      lev3 = lev3 %>% add_row(
        steam_factor = " ", 
        knowledge_domain = " ",
        knowledge_area = " ",
        tot_credits1 = 0,
        tot_credits2 = 0,
        tot_credits3 = 0,
        ymin = lev3$ymax, ymax = lev3$ymax, 
        ylab = lev3$ylab, 
        label = " ", label_nocred = " ",
        color = "white"
      )
  }
  
  lev1_g = ggplot(lev1) +
    ggtitle(str_wrap(courses_sum$label, 50)) +
    geom_rect(
      aes(
        ymin = 2, ymax = 3,
        xmin = ymin, xmax = ymax,
        fill = color
      ),
      color = "white"
    ) 
  
  lev1_g_label = geom_textpath(
        data = lev1, 
        aes(
          label = label,
          y = 2.5,
          x = ylab
        ),
        upright = TRUE, #fontface = "bold",
        size = 2.5, vjust = 0.5
    ) 
  
  lev1_g_label_nocred = geom_textpath(
        data = lev1,
        aes(
          label = label_nocred,
          y = 2.5,
          x = ylab
        ),
        upright = TRUE, #fontface = "bold",
        size = 3/fontsizescale, vjust = 0.5
    ) 
  lev1_g_label_abb = geom_textpath(
        data = lev1,
        aes(
          label = label_abb,
          y = 2.5,
          x = ylab
        ),
        upright = TRUE, #fontface = "bold",
        size = 3/fontsizescale, vjust = 0.5
    ) 
  
  lev2_g = geom_rect(
      data = lev2,
      aes(
        ymin = 3, ymax = 4,
        xmin = ymin, xmax = ymax,
        fill = color
      ),
      color = "white"
    ) 
  
  lev2_g_label = 
    geom_textpath(
      data = lev2,
      aes(
        label = label,
        y = 3.5,
        x = ylab
      ),
      upright = TRUE, #fontface = "bold",
      size = 2.75/fontsizescale, vjust = 0.5
    ) 
  lev2_g_label_nocred = 
    geom_textpath(
      data = lev2,
      aes(
        label = label_nocred,
        y = 3.5,
        x = ylab
      ),
      upright = TRUE, #fontface = "bold",
      size = 2.75/fontsizescale, vjust = 0.5
    ) 
  lev2_g_label_abb = 
    geom_textpath(
      data = lev2,
      aes(
        label = label_abb,
        y = 3.5,
        x = ylab
      ),
      upright = TRUE, #fontface = "bold",
      size = 2.75/fontsizescale, vjust = 0.5
    ) 
  
  lev3_g = geom_rect(
      data = lev3,
      aes(
        ymin = 4, ymax = 5,
        xmin = ymin, xmax = ymax,
        fill = color
      ),
      color = "white"
    ) 
  
  lev3_g_label = 
    geom_textpath(
      data = lev3,
      aes(
        label = label,
        y = 4.5,
        x = ylab
      ),
      upright = TRUE, 
      size = 2.75/fontsizescale, vjust = 0.5,
      text_only = TRUE
    )
  lev3_g_label_nocred = 
    geom_textpath(
      data = lev3,
      aes(
        label = label_nocred,
        y = 4.5,
        x = ylab
      ),
      upright = TRUE, 
      size = 2.75/fontsizescale, vjust = 0.5,
      text_only = TRUE
    )
    lev3_g_label_abb = 
    geom_textpath(
      data = lev3,
      aes(
        label = label_abb,
        y = 4.5,
        x = ylab
      ),
      upright = TRUE, 
      size = 2.75/fontsizescale, vjust = 0.5,
      text_only = TRUE
    )
  
  g = if (labelabb == TRUE) {
      g = if(nrow(lev2) != 0 & nrow(lev3) != 0) {
        lev1_g + 
        lev2_g + 
        lev3_g +
        lev1_g_label_abb +
        lev2_g_label_abb +
        lev3_g_label_abb
      } else if (nrow(lev2) != 0 & nrow(lev3) == 0) {
        lev1_g + 
        lev2_g + 
        lev1_g_label_abb +
        lev2_g_label_abb 
      } else {
        lev1_g +
        lev1_g_label_abb
      }
    g
  } else if(
    filter(
      courses, curricula_id == id
    )$credits_specification[1] == "Yes"
  ) {
      g = if(nrow(lev2) != 0 & nrow(lev3) != 0) {
        lev1_g + 
        lev2_g + 
        lev3_g +
        lev1_g_label +
        lev2_g_label +
        lev3_g_label
      } else if (nrow(lev2) != 0 & nrow(lev3) == 0) {
        lev1_g + 
        lev2_g + 
        lev1_g_label +
        lev2_g_label 
      } else {
        lev1_g +
        lev1_g_label
      }
    g
    } else if (filter(
      courses, curricula_id == id
    )$credits_specification[1] == "No" ) {
      g = if(nrow(lev2) != 0 & nrow(lev3) != 0) {
        lev1_g + 
        lev2_g + 
        lev3_g +
        lev1_g_label_nocred +
        lev2_g_label_nocred +
        lev3_g_label_nocred
      } else if (nrow(lev2) != 0 & nrow(lev3) == 0) {
        lev1_g + 
        lev2_g + 
        lev1_g_label_nocred +
        lev2_g_label_nocred 
      } else {
        lev1_g +
        lev1_g_label_nocred
      }
    g + labs(caption = "Credit information per subject\nnot available for this curricula.")
    } else g
  
  g +
    scale_fill_identity() +
    scale_y_continuous(
      limits = c(0,5),
      expand = expansion(mult = c(0, -0.15))
    ) +
    coord_polar() +
    theme_bw() +
    theme(
      text = element_text(size = 12),
      panel.grid = element_blank(),
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      panel.border = element_blank(),
      legend.title = element_blank(),
      plot.title = element_text(
        hjust = 0.5, 
        margin = margin(0,0,0,0)
      )
    )
}
```

# Sunburst - static

```{r, fig.showtext=TRUE}
# fontsizescale = 1.3
# missing = c(3,6,26,29,34,40)
# fontsizescale = 1.1, labelabb = TRUE
missing = c(7,8,16,17,31,47)
# fontsizescale = 1.4, labelabb = TRUE
# missing = c(5)
lapply(missing, function(x){
# lapply(1:nrow(curricula), function(x){
  sunburst_plot(
    id = x,
    fontsizescale = 1.1,
    labelabb = TRUE
  )
  ggsave(
    filename = paste0("plots/sb_curricula_x", x, ".png"),
    width = 16, height = 18.5, units = "cm", device = ragg::agg_png()
  )
  dev.off()
})
```
 
 
# Barchart

```{r, fig.showtext = TRUE}
curricula_steamt_summary = courses %>% 
  filter(credits_specification == "Yes") %>% 
  mutate(
    degree_std = case_when(str_starts(degree, "BSc") ~ "B.Sc.", TRUE ~ "M.Sc.")
  ) %>% 
  group_by(curricula_id, curricula_name, steam_category) %>% 
  summarise(
    steamt_credits = sum(credits),
    hei_name = first(hei_name),
    degree = first(degree_std), 
    joint_program = first(joint_program)
  ) %>% 
  mutate(
    steamt_science_share = sum(steamt_credits[steam_category=="Science"], na.rm=T)/sum(steamt_credits, na.rm=T),
    steam_factor = fct_relevel(
        fct_expand(
          steam_category, 
          "Science", "Technology", 
          "Engineering", "Arts",
          "Mathematics", "Transversal"
        ),
        "Science", "Technology", "Engineering",
        "Arts", "Mathematics", "Transversal"
      ),
    color = case_when(
      steam_category == "Science" ~ steamt_palette[1],
      steam_category == "Technology" ~ steamt_palette[2],
      steam_category == "Engineering" ~ steamt_palette[3],#"#0C4690",
      steam_category == "Arts" ~ steamt_palette[4],
      steam_category == "Mathematics" ~ steamt_palette[5],
      steam_category == "Transversal" ~ steamt_palette[6]
    )
  )

msc = curricula_steamt_summary %>% 
  filter(degree == "M.Sc.", joint_program == "No") %>% 
  mutate(
    curricula_name = str_replace_all(curricula_name, "MSc", "M.Sc.")
    ) %>% 
  mutate(
    curricula_name = str_replace_all(curricula_name, "LLM", "LL.M.")
    )
ggplot(msc) +
  geom_col(
    aes(
      x = steamt_credits,
      y = reorder(
        as.factor(curricula_id),
        steamt_science_share,
        descending = FALSE
      ),
      fill = steam_factor, 
    ), position = position_fill(reverse = TRUE)
  ) +
  scale_fill_manual("", values = steamt_palette) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_discrete(
    labels = ~ str_wrap(paste0(
      msc$hei_name[match(.x, msc$curricula_id)],
      " | ", 
      msc$curricula_name[match(.x, msc$curricula_id)]
    ), 50)
  ) +
  ggtitle("Masters curricula per STEAMT category") +
  guides(
    fill = guide_legend(
      nrow = 1, 
      keywidth = grid::unit(15, "mm"),
      label.hjust = 0.5,
      label.position = "bottom"
  )) +
  theme_bw() +
  theme(
    text = element_text(family = coorpfont, size = 11),
    axis.title = element_blank(),
    axis.text = element_text(size = 9),
    legend.position = "bottom",
    legend.justification = "right",
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5)
  ) 

ggsave(filename = paste0("plots/bar_curricula_msc.png"),
    width = 15, height = 23.3, units = "cm")

msc_joint = curricula_steamt_summary %>% 
  filter(degree == "M.Sc.", joint_program == "Yes") %>% 
  mutate(curricula_name = str_replace_all(curricula_name, "MSc", "M.Sc."))
ggplot(msc_joint) +
  geom_col(
    aes(
      x = steamt_credits,
      y = reorder(
        as.factor(curricula_id),
        steamt_science_share,
        descending = FALSE
      ),
      fill = steam_factor, 
    ), position = position_fill(reverse = TRUE)
  ) +
  scale_fill_manual("", values = steamt_palette, drop = FALSE) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_discrete(
    labels = ~ paste0(
      str_wrap(
        msc_joint$hei_name[match(.x, msc_joint$curricula_id)],
        60),
      "\n| ", 
      str_wrap(
        msc_joint$curricula_name[match(.x, msc_joint$curricula_id)],
        50)
    )
  ) +
  ggtitle("Joint Masters curricula per STEAMT category") +
  guides(
    fill = guide_legend(
      nrow = 1, 
      keywidth = grid::unit(15, "mm"),
      label.hjust = 0.5,
      label.position = "bottom"
  )) +
  theme_bw() +
  theme(
    text = element_text(family = coorpfont, size = 11),
    axis.title = element_blank(),
    axis.text = element_text(size = 10),
    legend.position = "bottom",
    legend.justification = "right",
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5)
  ) 

ggsave(filename = paste0("plots/bar_curricula_msc_joint.png"),
    width = 16.5, height = 7.5, units = "cm")

bsc = curricula_steamt_summary %>% 
  filter(degree == "B.Sc.") %>% 
  mutate(curricula_name = str_replace_all(curricula_name, "BSc", "B.Sc."))
ggplot(bsc) +
  geom_col(
    aes(
      x = steamt_credits,
      y = reorder(
        as.factor(curricula_id),
        steamt_science_share,
        descending = FALSE
      ),
      fill = steam_factor, 
    ), position = position_fill(reverse = TRUE)
  ) +
  scale_fill_manual("", values = steamt_palette) +
  scale_x_continuous(labels = scales::percent) +
  scale_y_discrete(
    labels = ~ paste0(
      bsc$hei_name[match(.x, bsc$curricula_id)],
      "\n| ",
      bsc$curricula_name[match(.x, bsc$curricula_id)]
    )
  ) +
  ggtitle("Bachelors curricula per STEAMT category") +
  guides(
    fill = guide_legend(
      nrow = 1, 
      keywidth = grid::unit(15, "mm"),
      label.hjust = 0.5,
      label.position = "bottom"
  )) +
  theme_bw() +
  theme(
    text = element_text(family = coorpfont, size = 11),
    axis.title = element_blank(),
    axis.text = element_text(size = 10),
    legend.position = "bottom",
    legend.justification = "right",
    plot.title.position = "plot",
    plot.title = element_text(hjust = 0.5)
  )

ggsave(filename = paste0("plots/bar_curricula_bsc.png"),
    width = 16.5, height = 9, units = "cm")

curricula_steamt_summary %>% 
  group_by(steam_factor, color) %>% 
  summarise(
    credits = sum(steamt_credits)
  ) %>% 
  ungroup() %>% 
  mutate(
    frac = credits/sum(credits),
    ymax = cumsum(frac),
    ymin = c(0, head(ymax, n = -1)),
    label = paste0(
      "<span style = 'font-family:",
      coorpfont,";'>",
      steam_factor,"<br>",
      round(100*frac, 1), "%</span>"),
    labelPosition = (ymax+ymin)/2
  ) %>% 
  ggplot() +
  aes(
    ymax = ymax, ymin = ymin,
    xmax = 4, xmin = 3,
    fill = steam_factor
  ) +
  geom_rect() +
  geom_richtext(
    x = 3.5,
    aes(y = labelPosition, label = label),
    size = 4,
    # remove label background and outline
    fill = NA, label.color = NA,
    # remove label padding, since we have removed the label outline
    label.padding = grid::unit(rep(0, 4), "pt") 
  ) +
  coord_polar(theta = "y") +
  xlim(c(2, 4)) +
  scale_fill_manual(
    "",
    values = steamt_palette
  ) +
  theme_void() +
  theme(
    text = element_text(
      family = coorpfont,
      size = 11
    ),
    panel.background = element_rect(
      fill = "white", color = NA
    ),
    legend.position = "none"
  ) 
ggsave(
  filename = "plots/doughnut_steamt.png",
  width = 11, height = 11, units = "cm",
  device = ragg::agg_png()
)
knitr::plot_crop("plots/doughnut_steamt.png")
```
 
# Knowledge domain charts

```{r}
curricula_steamt_kd_summary = courses %>% 
  mutate(
    degree_std = case_when(str_starts(degree, "BSc") ~ "B.Sc.", TRUE ~ "M.Sc.")
  ) %>% 
  # filter(degree == "MSc") %>%
  group_by(steam_category, knowledge_domain, degree_std) %>% 
  summarise(no_curricula = n_distinct(curricula_id)) %>%
  mutate(
    steam_factor = fct_relevel(
        fct_expand(
          steam_category, 
          "Science", "Technology", 
          "Engineering", "Arts",
          "Mathematics", "Transversal"
        ),
        "Science", "Technology", "Engineering",
        "Arts", "Mathematics", "Transversal"
      )
  )

ggplot(curricula_steamt_kd_summary) +
  geom_col(aes(
    # y = fct_explicit_na(
    #   reorder(knowledge_domain, no_curricula),
    #   na_level = "Uncategorized"
    # ),
    y = fct_explicit_na(
      knowledge_domain,
      na_level = "Uncategorized"
    ),
    x = no_curricula,
    fill = degree_std
    ), 
    # position = "stack"
    position = position_dodge(preserve = "single")
  ) +
  scale_fill_manual("Degree", values = c(steamt_palette[2], steamt_palette[5])) +
  scale_x_continuous(n.breaks = 6) +
  scale_y_discrete(limits=rev) +
  facet_wrap(
    ~steam_factor,
    scales = "free", nrow = 3
  ) +
  labs(title = "Number of curricula per knowledge domain") +
  theme_bw() +
  theme(
    axis.title = element_blank(),
    text = element_text(family = coorpfont, size = 11),
    legend.position = "top",
    legend.justification = "center",
    plot.title = element_text(hjust = 0.5)
  )

ggsave(filename = paste0("plots/bar_knowledge_domain.png"),
    width = 16, height = 16, units = "cm")


curricula %>% 
  mutate(
    degree_std = case_when(str_starts(degree, "BSc") ~ "B.Sc.", TRUE ~ "M.Sc.")
  ) %>% 
  count(degree_std) %>% 
  ggplot() +
  aes(
    y = degree_std,
    x = n,
    fill = degree_std,
    label = scales::percent(prop.table(n))
  ) +
  geom_col() +
  geom_text(nudge_x = -2, family = coorpfont) +
  labs(title = "Number of curricula per degree type") +
  scale_fill_manual("", values = c(steamt_palette[2], steamt_palette[5])) +
  theme_bw() +
  theme(
    text = element_text(family = coorpfont, size = 11),
    legend.position = "none",
    axis.title = element_blank(),
    plot.title = element_text(hjust = 0.5)
  )

ggsave(filename = paste0("plots/bar_degree.png"),
    width = 13, height = 5, units = "cm")
```


 
## Knowledge area charts

```{r}
curricula_steamt_ka_summary = courses %>% 
  mutate(
    degree_std = case_when(str_starts(degree, "BSc") ~ "B.Sc.", TRUE ~ "M.Sc.")
  ) %>% 
  # filter(degree == "MSc") %>%
  group_by(steam_category, knowledge_domain, knowledge_area, degree_std) %>% 
  summarise(no_curricula = n_distinct(curricula_id)) %>%
  mutate(
    steam_factor = fct_relevel(
        fct_expand(
          steam_category, 
          "Science", "Technology", 
          "Engineering", "Arts",
          "Mathematics", "Transversal"
        ),
        "Science", "Technology", "Engineering",
        "Arts", "Mathematics", "Transversal"
      )
  )

know_area_plot = function(steamtcat = "Science") {
  curricula_steamt_ka_summary %>% 
    filter(steam_factor == steamtcat) %>% 
  ggplot() +
  geom_col(aes(
    y = fct_explicit_na(
      reorder(knowledge_area, no_curricula),
      na_level = "Uncategorized"
    ),
    x = no_curricula,
    fill = degree_std
    ), 
    position = position_dodge(preserve = "single")
  ) +
  scale_fill_manual("Degree", values = c(steamt_palette[2], steamt_palette[5])) +
  facet_wrap(
    ~ knowledge_domain,
    scales = "free"
  ) +
  labs(title = paste0(steamtcat, " - Number of curricula per knowledge area")) +
  theme_bw() +
  theme(
    text = element_text(family = coorpfont),
    axis.title = element_blank(),
    axis.text = element_text(size = 9),
    legend.position = "top",
    legend.justification = "center",
    plot.title = element_text(hjust = 0.5)
  )

ggsave(filename = paste0("plots/bar_knowledge_area_",steamtcat,".png"),
    width = 20, height = 16, units = "cm")
}

know_area_plot(steamtcat = "Science")
know_area_plot(steamtcat = "Technology")
know_area_plot(steamtcat = "Engineering")
know_area_plot(steamtcat = "Arts")
know_area_plot(steamtcat = "Mathematics")
know_area_plot(steamtcat = "Transversal")
```

# Map

```{r}
library(rnaturalearth)
countries = ne_countries(returnclass = "sf", scale = "large")
crs = "+proj=natearth2 +datum=WGS84 +no_defs +over"
crs_eu = 3035
zoom_buffer = st_sfc(
  st_point(c(4,53)),
  crs = 4326
) %>% 
  st_transform(crs_eu) %>% 
  st_buffer(2200000) %>% 
  st_bbox() %>% 
  st_as_sfc()
```

```{r}
hei_curricula = hei_sf %>% 
  left_join(curricula)
curricula_country = hei_curricula %>% 
  mutate(coutry = case_when(
    country == "US" ~ "Unites States of America", 
    TRUE ~ country
  )) %>% 
  count(country) %>% 
  st_drop_geometry() %>% 
  left_join(select(countries, country = name_en)) %>% 
  st_as_sf()
curricula_hei = curricula %>% 
  full_join(hei_sf) %>% 
  count(hei_id) %>% 
  left_join(hei_sf) %>%
  st_as_sf()
```

```{r}
ggplot() +
  geom_sf(
    data = countries,
    fill = steamt_palette[4],
    color = NA
  ) +
  theme_void() +
  theme(
    text = element_text(family = coorpfont),
    panel.background = element_rect(
      fill = "white", color = NA,
    ),
    panel.border = element_rect(
      fill = NA, color = "black", size = 1
    ),
    legend.position = c(0.1,0.5)
  ) +
  geom_sf(
    data = curricula_country,
    aes(fill = n), color = NA
  ) +
  geom_sf(
    data = st_jitter(curricula_hei, factor = 0.001), 
    shape = 21, stroke = 0.5, 
    alpha = 0.8,
    fill = "grey30",
    color = "white",
    aes(size = n)
  ) +
  scale_fill_gradient2(
    "No. of\ncurricula\nper country",
    low = steamt_palette[3], 
    mid = steamt_palette[1], 
    high = steamt_palette[6],
    midpoint = 4, 
    n.breaks = 8
  ) +
  scale_size(
    "No. of\ncurricula\nper HEI",
    range = c(2,4),
    breaks = c(1,2)
  ) +
  guides(size = guide_legend(order = 2),
         fill = guide_legend(order = 1)) +
  coord_sf(
    crs = crs_eu, expand = FALSE, clip = "on",
    xlim = c(
      st_bbox(st_transform(zoom_buffer, crs_eu))['xmin'],
      st_bbox(st_transform(zoom_buffer, crs_eu))['xmax']
    ),
    ylim = c(
      st_bbox(st_transform(zoom_buffer, crs_eu))['ymin'],
      st_bbox(st_transform(zoom_buffer, crs_eu))['ymax']
    )
  ) 

ggsave(filename = "plots/map_eu_uk.png",
    width = 13, height = 13, units = "cm")
```

# Table 

```{r}
curr_list = curricula %>% 
  left_join(hei) %>% 
  mutate(
     degree_std = case_when(str_starts(degree, "BSc") ~ "BSc", TRUE ~ "MSc"),
    country = case_when(
      country == "UK" ~ "United Kingdom", 
      country == "US" ~ "U.S.A.", 
      TRUE ~ country
    )
  ) %>% 
  select(curricula_name, hei_name, degree_std, city, country)

curr_list %>% 
  write_excel_csv(file = "plots/curricula_list.csv")
```

